Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations

### 2020-09-07 paper.Rnw
working on updating to the training dataset Heike is publishing

# Load the hamby data
bullet_train <- read.csv("../data/hamby173and252_train.csv")
bullet_test <- read.csv("../data/hamby224_test.csv")

>>>>

# Load the bullet matching training data and make some adjustments:
#   1. filter out observations know to have tank rash
#   2. exclude features not used to train the rtrees random forest 
#   3. add a variable with the random forest probability in support of a match
#   4. change the name of the same_source variable to match the test data
#   5. reorder the variables
bullet_train_temp <- read.csv("data-bullet-train.csv") %>%
  #filter(land_id1 == "Hamby173-BrUnk-B2-L1")
  select(-lag,-abs_lag,-signature_length) %>%
  mutate(
    case = factor(1:n()),
    rfscore = predict(rtrees, bullet_train_temp %>% select(rownames(rtrees$importance)), type = "prob")[, 2]
  ) %>%
  rename("samesource" = "same_source") %>%
  select(case, land_id1, land_id2, everything())

# Load the bullet test data
bullet_train <- read.csv("../data/hamby173and252_train.csv")
bullet_test <- read.csv("data-bullet-test.csv")

### 2020-09-07 paper.tex
working on updating to the training dataset Heike is publishing

In response, \citet{hare:2016} proposed an automated machine learning method for bullet matching to complement a visual inspection by firearm examiners. Based on high-resolution topological scans of land engraved areas, \citet{hare:2016} obtain signatures of striations from two bullet lands (\autoref{fig:figure-09}). Nine features quantifying the similarity of signatures, such as the cross-correlation function, the distance between signatures, and the number of matching striae, are extracted and used to train a random forest (available in the \emph{bulletxtrctr} R package) to determine the probability of a comparison resulting from the same source (matching signatures) or from different sources (non-matching signatures). \kge{See the supporting information for additional information on the data.} The model was trained on a set of scans of bullets from the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009}, which includes 83028 land-to-land comparisons.

>>>>

In response, \citet{hare:2016} proposed an automated machine learning method for bullet matching to complement a visual inspection by firearm examiners. Based on high-resolution topological scans of land engraved areas, \citet{hare:2016} obtain signatures of striations from two bullet lands (\autoref{fig:figure-09}). Nine features quantifying the similarity of signatures, such as the cross-correlation function, the distance between signatures, and the number of matching striae, are extracted and used to train a random forest (available in the \emph{bulletxtrctr} R package) to determine the probability of a comparison resulting from the same source (matching signatures) or from different sources (non-matching signatures). \kge{See the supporting information for additional information on the data.} The model was trained on a set of scans of bullets from the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009}, which includes 83436 land-to-land comparisons.
